### 2020-11-22 README.Rmd
Working MCDA but now need data files to reflect current structure

```{r example}
# a minimal example
starttime <- as.character(Sys.time())
library(aMSE)
library(rutilsMH)
library(makehtml)
# Obviously you should modify the resdir to suit your own computer
resdir <- "./../../A_code/aMSEUse/out/run1"
dirExists(resdir,make=TRUE,verbose=TRUE)
# The following function calls will ensure that there is a control.csv,
# a zone1.csv, and a zone1sau2pop6.csv or population data file 
# in the data directory, which in this case is the same as the resdir
ctrlfiletemplate(resdir)
zonefiletemplate(resdir)
datafiletemplate(numpop=6,resdir,filename="zone1sau2pop6.csv")

ctrl <- checkctrldat(resdir)
runname <- ctrl$runlabel
zone1 <- readzonefile(resdir,ctrl$zonefile)
glb <- zone1$globals     # glb without the movement matrix
constants <- readdatafile(glb$numpop,resdir,ctrl$datafile)

out <- setupzone(constants,zone1) # make operating model
zoneC <- out$zoneC
zoneD <- out$zoneD
glb <- out$glb        # glb now has the movement matrix
product <- out$product     # important bits usually saved in resdir
          # did the larval dispersal level disturb the equilibrium?
regDe <- testequil(zoneC,zoneD,glb)

resfile <- setuphtml(resdir)# prepare to save and log results

plotproductivity(resdir,product,glb)
biology_plots(resdir, glb, zoneC)
numbersatsize(resdir, glb, zoneD)

endtime <- as.character(Sys.time())

reportlist <- list(runname=runname,
                   starttime=starttime,endtime=endtime,
                   zoneC=zoneC, zoneD=zoneD, product=product,
                   glb=glb,constants=constants)

runnotes <- "This is a bare-bones example."
# If you unhash the make_html call it will generate a local website 
# inside resdir and open it so you can see the results so far.
# make_html(replist=reportlist,resdir=resdir,width=500,
#          openfile=TRUE,runnotes=runnotes,verbose=FALSE,
#          packagename="aMSE",htmlname="testrun")
```

>>>>

```{r example, echo=TRUE}
# a constant TAC example
starttime <- (Sys.time())
library(aMSE)
library(rutilsMH)
library(makehtml)
library(knitr)
# Obviously you should modify the resdir to suit your own computer
if (dir.exists("c:/Users/User/DropBox")) {
  ddir <- "c:/Users/User/DropBox/A_code/"
} else {
  ddir <- "c:/Users/Malcolm/DropBox/A_code/"
}
resdir <- paste0(ddir,"aMSEUse/conddata/generic2")  # data and results directory
dirExists(resdir,make=TRUE,verbose=TRUE)
# equilibrium zone -------------------------------------------------------------
# You now need to ensure that there is, at least, a control.csv, zone1.csv
# and region1.csv file in the data directory plus some other data .csv files
# depending on how conditioned you want the model to be. Templates for the
# correct format can be produced using ctrlfiletemplate(), datafiletemplate(),
# and zonefiletemplate.  In the meantime it is easier to use the included 
# data files. The original csv files are included in the data-raw directory

# Many changes now require the data files to be updated and tested, but that will 
# happen soon.

```
